---
title: "recidivism"
author: "thibault FUCHEZ"
date: "13/05/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("C:/Users/arkan/Desktop/Memoire-M1/applications.R")
```

```{r}
source("functions_UC.R")
```

# prepa datas

```{r}
recid <-
  read.csv(
    "recidivism.csv",
    header = TRUE,
    sep = ",",
    stringsAsFactors = T
  )
data <-   read_csv("recidivism.csv")
```

```{r}
#temps passé en prison 

data$time_jailed <- data[,"c_jail_out"] - data[,"c_jail_in"]
recid$time_jailed <- data$time_jailed
```

```{r}
recid<- recid[,c("sex","age_cat","race","juv_fel_count","juv_misd_count","juv_other_count", "priors_count","c_charge_degree","time_jailed","is_violent_recid")]
```

```{r}
recid$time_jailed <- recid$time_jailed / (60*24)
recid$time_jailed <- as.difftime(unlist(recid$time_jailed), units = "days")
recid$time_jailed <- abs(recid$time_jailed)
```

```{r}
sum(is.na(recid$time_jailed))
sum(is.na(recid))
recid <- na.omit(recid)
recid$is_violent_recid <- as.factor(recid$is_violent_recid)
```

```{r}
recid <- recid[,c(10, 1:9 )]
```

# first models

```{r}
datRecid <- split_standard(data =  recid, y =  "is_violent_recid", mod = "standard")
```

```{r}
Modrecid <- models(y = "is_violent_recid",
                   data = datRecid$train,
                   costSvm = 0.25,
                   kernSvm = "radial",
                   priors(dat = datRecid$train, "is_violent_recid"))
```

```{r}
PredRec1 <- predictions(models = Modrecid, datas = datRecid)
```

```{r}
KablesPerf(pred = PredRec1, dat = datRecid$test, y = "is_violent_recid")
```

```{r}
par(mfrow=c(1,1))
AllRoc(predic = PredRec1, dataCl = datRecid$test$is_violent_recid)
```

# remedies

## Datas prepocessing : 

### Upsample

```{r}
DatRecUS <- resamp_res(recid, mod = "US")
```

```{r}
DatRecUS[[1]][[2]]
```

### ROSE

```{r}
str(recid2)
```

```{r}
recid2 <- as.data.frame(sapply(recid[,c(5:8)], function(x) as.numeric(x)))
recid2 <- cbind(recid[,c(1:4, 9:10)], recid2)
```

```{r}
str(recid2)
```

```{r}
recid2$time_jailed <- as.numeric(recid2$time_jailed)
recid$time_jailed <- as.numeric(recid2$time_jailed)
str(recid2$time_jailed)
```

```{r}
roseRecid <- ROSE(is_violent_recid~. , recid)
RoseDataRecid <- roseRecid$data
```

```{r}
plot(RoseDataRecid$is_violent_recid)
```

```{r}
datasRoseRecid<- split_standard(RoseDataRecid, "is_violent_recid", mod = "standard")
```

```{r}
ModelsRoseRecid <- models(y = "is_violent_recid",
                          data = datasRoseRecid$train,
                          prior = priors(datasRoseRecid$train,
                                         "is_violent_recid"))
```

```{r}
predRoseRecid <- predictions(models = ModelsRoseRecid,
                             datas = datasRoseRecid)
```

```{r}
KablesPerf(pred = predRoseRecid, dat = datasRoseRecid$test,
            y =  "is_violent_recid")
```

```{r}
AllRoc(predRoseRecid, dataCl = datasRoseRecid$test$is_violent_recid) 
```

### SMOTE-NC

```{r}
#TESTSMNC <- resamp_res(recid, mod = "SMOTE-NC")
```

```{r}
#1h et 7 min à tourner !!!!!!!!
Resamp11 <- SMOTE_NC(data = recid, outcome = "is_violent_recid")
```

```{r}
plot(Resamp11$is_violent_recid)
plot(recid$is_violent_recid)
```

```{r}
datrecSmc <- split_standard(data = Resamp11, y = "is_violent_recid",
                            mod = "standard")
```

```{r}
ModRecidSMC <- models(data = datrecSmc$train, y = "is_violent_recid",
                      prior = priors(dat = datrecSmc$train,
                                     y = "is_violent_recid"))
```

```{r}
predRecSmc <- predictions(models = ModRecidSMC, datas = datrecSmc)
```

```{r}
KablesPerf(pred = predRecSmc, dat = datrecSmc$test, y ="is_violent_recid", listPred = "lr", captionCM = "test", captionPerf = "test", mod = "lr")
```

```{r}
AllRoc(predic = predRecSmc, dataCl = datrecSmc$test$is_violent_recid)
```

# Learning method

## Tune parameters

## Cost sensitive learning

```{r}
priors(datRecid$train, "is_violent_recid")
```

```{r}
ModRecSens <- models(y = "is_violent_recid", data = datRecid$train,
               prior = priors(datRecid$train, "is_violent_recid"),
               CWSvm = c("0" = 1, "1" = 1),
               costSvm = 0.25,
               kernSvm = "radial",
               CWRf = c(1, 10))
```

```{r}
PredRecSens <- predictions(models = ModRecSens, datas = datRecid)
```

```{r}
KablesPerf(PredRecSens, datRecid$test, "is_violent_recid")
```

Autres tests : 

```{r}
TestCost2 <- train(is_violent_recid~.,
                  data = datRecid$train,
                  method = "svmRadial",
                  class.weights = c("0" = 1, "1" = 10)
                  )
```

```{r}
PredTestCost2 <- predict(TestCost2, datRecid$test)
PredTestCost2
```

```{r}
perf.measure(PredTestCost2, datRecid$test, "is_violent_recid")
```

*test2 

```{r}
TestCost3 <- train(is_violent_recid~.,
                  data = datRecid$train,
                  method = "svmRadial",
                  class.weights = c("0" = 1, "1" = 20)
                  )
```

```{r}
PredTestCost3 <- predict(TestCost3, datRecid$test)

perf.measure(PredTestCost3, datRecid$test, "is_violent_recid")
```

# Post processing

## Alternate cutoff

```{r}
priors(recid, "is_violent_recid")
```

```{r}
plot(recid$is_violent_recid)
```

### Visualization of the errors depending threshold for belonging to thepositive class

```{r}
par(mfrow=c(2,2))
evoSeuil(PredRec1$predLda, datRecid$test$is_violent_recid, datRecid$test, "posterior")
evoSeuil(PredRec1$predlog$prob, datRecid$test$is_violent_recid, datRecid$test, "autres")
evoSeuil(attr(PredRec1$predSvm, "probabilities")[,1],
         datRecid$test$is_violent_recid, datRecid$test, "autres")
evoSeuil(PredRec1$predrf$prob[,2], datRecid$test$is_violent_recid, datRecid$test, "autres")
```

```{r}
 averageRec <- sum(datRecid$train$is_violent_recid=="1")/nrow(datRecid$train)
```

```{r}
attr(PredRec1$predSvm, "probabilities")
```

### Predictions with new threshold : 

```{r}
predRecldaseuil <- changeSeuil(PredRec1$predLda, datRecid$test$is_violent_recid, datRecid$test, 0.12, "posterior")

predReclogseuil <- changeSeuil(PredRec1$predlog$prob, datRecid$test$is_violent_recid, datRecid$test, 0.12, "autres")

predRecrfseuil <- changeSeuil(PredRec1$predrf$prob[,2], datRecid$test$is_violent_recid, datRecid$test, 0.12, "autres")

predRecsvmseuil <- changeSeuil(attr(PredRec1$predSvm, "probabilities")[,1], datRecid$test$is_violent_recid, datRecid$test, 0.12, "autres")

listPredseuilRec <- list(predRecrfseuil, predReclogseuil,
                      predRecldaseuil, predRecsvmseuil)
```

```{r}
KablesPerf2(pred = PredRec1, dat = datRecid$test, y = "is_violent_recid", listPred = listPredseuilRec)
```

# Notes 

Voc: 

battery : coups et blessure
degree charge : F fellony (crime et délit) / M midemeanor (infraction)
priors : antécédents

tps passé en prision : 

Remplacer NA par moyenne du tps passé. mettre en valeur absolur car parfois inversé. 

```{r}
recidWhat <-
  read.csv(
    "recidivism.csv",
    header = TRUE,
    sep = ",",
    stringsAsFactors = T
  )
```

```{r}
str(recidWhat$is_recid)
sum(recidWhat$is_violent_recid)/nrow(recidWhat)
```

Gros boulet!!!!!!!!!!!!!!!!!!!!!!!!!!!!

```{r}
priors(recid, "is_recid")
```

```{r}
priors(recid, "is_violent_recid")
```

*Support Vector Machines with Class Weights (method = 'svmRadialWeights')

For classification using package kernlab with tuning parameters:

Sigma (sigma, numeric)

Cost (C, numeric)

Weight (Weight, numeric)

*Regularized Logistic Regression (method = 'regLogistic')

For classification using package LiblineaR with tuning parameters:

Cost (cost, numeric)

Loss Function (loss, character)

Tolerance (epsilon, numeric)


